% This is the scientific article needed for the Electronic Business course
%
\documentclass{llncs}
%
\usepackage{float}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}

%
\begin{document}
%
\pagestyle{headings}  % switches on printing of running heads
%
% second contribution with nearly identical text,
% slightly changed contribution head (all entries
% appear as defaults), and modified bibliography
%
\title{Automatic Wine Quality Classification based on Physicochemical Tests }

\author{Miguel Araújo e André Fernandes}

\institute{Faculty of Engineering, Porto University, Rua Dr Roberto Frias, S/N, Porto, Portugal}

\maketitle

\begin{abstract}
Amazing abstract.

\keywords{machine learning, classification, data mining, regression analysis}
\end{abstract}

\section{Introduction}
 Short description of the domain problem to which the data set belongs

What is/are the Data Mining (DM) problem(s) addressed in your study  (Classification/Clustering Rules etc..)

Determine business objective; data mining goals.

\section{Dataset analysis}
Short intro (explain we have red and white and that we are going to analyze them separately and together)

Question whether to treat output as discrete or continuous.

Dataset breakdown; classic statistical approach (averages, std. dev., min, max, box charts, input correlations)

Correlations to output.

Data quality.

Data preparation.

\section{Classification approaches}
Referir alguns algoritmos/métodos que vamos seleccionar para aplicar no resto do trabalho.

\subsection{One Decision Tree approach}
ID3; C4.5; Random Forest

\subsection{One Network approach}
Bayesian network ; feedforward NN



\section{Test methodology}
How are we evaluating? Splitting the dataset (about 70/30) and applying several 

\section{Conclusions}
Preliminary results, optimistic? 


%
% ---- Bibliography ----
%
\bibliographystyle{splncs}.
\begin{thebibliography}{}
%
\bibitem[1]{adauctions}
Patrick R. Jordan, Akshat Kaul, and Michael P. Wellman:
The Ad Auctions Game
for the 2010 Trading Agent Competition
[Specification for Server Version 10.1.0.0]
(May 6, 2010)
\end{thebibliography}
\end{document}
